The Shape and Color of Politics

### 2023-10-23 chapter_2/src/slides/slides.qmd
updating the slides a bit

---
title: "The Shape and Color of Politics"
author:
  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
  revealjs:
    multiplex: true
    embed-resources: true
    theme: [dark, ../../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: false
    slide-number: false
    progress: false
    menu: false
    toc: false
    #toc-depth: 2
    slide-level: 5
    bibliography: ../../../assets/candidate_support_chapter_references.bib   
    self-contained: true
    output-file: color-book.html
    fig-responsive: false
    margin: 0.1
execute:
  echo: false
  freeze: true
  eval: true
  cache: true
nocite: |
  @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017,
---

@@

@@

![[Shell]()](../../assets/slides/imgs/shell.png){#fig-shell width=6.5in}

@@

```{mermaid}
%%| label: fig-shell-color
%%| fig-cap: Associative memory
%%| eval: true
flowchart LR;

A["Yellow"]
A --> B["Banana"]
A --> C["Rubber duck"]
A --> D["Shell"]
A --> E["Leaves"]
```

```{mermaid}
%%| label: fig-shell-affect
%%| fig-cap: Object evaluation
%%| eval: true
flowchart LR;

A["Yellow"]
A -.-> B["Banana"]
A -.-> C["Rubber duck"]
A --> D["Shell"]
A -.-> E["Leaves"]
D --> F["Avoid"]
```

<!--
---

![[Kirkland Signature]()](../../assets/slides/imgs/kirkland.svg){#fig-kirkland width=6.5in}

![[BP]()](../../assets/slides/imgs/bp.png){#fig-bp width=6.5in}

-->
![[Example of brand UI]()](../../assets/slides/imgs/green_bubble.jpeg){.absolute left=100 width=4.5in #fig-brand-ui}
![[The great divide]()](../../assets/slides/imgs/green_bubble_funny.png){.absolute right=100 width=4.5in #fig-brand-divide}

@@

@@

{{< include ../../../assets/_theory.qmd >}}

@@

# Define colors to detect
    #* White
        #** Not defined. Default for colorDetector()
    #* Red
republican_red = [232, 27, 35] # target color
red_lower = [93, 9, 12] # lower end of spectrum for red
red_higher = [237, 69, 75] # higher end of spectrum for red

>>>>

---
title: "The Shape and Color of Politics"
author:
    - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
    simpledarkjs-revealjs:
        multiplex: true
        output-file: color-book.html
        slide-level: 5
        transition: none
bibliography: ../../../assets/candidate_support_chapter_references.bib
execute:
    echo: false
    freeze: true
    eval: true
    cache: true
nocite: |
    @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017
---

@@

![Aaron Bashir (R), PA-3](../../assets/slides/imgs/bashir.webp){#fig-bashir .absolute left=0 top=100}
![Dwight Evans (D), PA-2](../../assets/slides/imgs/evans.webp){#fig-evans .absolute right=0 bottom=100}

@@

![Nebraska](../../assets/slides/imgs/nebraska.jpg){#fig-nebraska width=6.5in}

@@

![[Example of brand UI]](../../assets/slides/imgs/green_bubble.jpeg){.absolute left=100 width=4.5in #fig-brand-ui}
![[The great divide]](../../assets/slides/imgs/green_bubble_funny.png){.absolute right=100 width=4.5in #fig-brand-divide}

@@

![[1924 Election Map](https://collections.leventhalmap.org/search/commonwealth:q524n296b)](../../assets/slides/imgs/election_map.jpg){#fig-1924-map}

![[1976 Election Map](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.washingtonpost.com%2Fnews%2Fthe-fix%2Fwp%2F2016%2F11%2F08%2Fred-vs-blue-a-brief-history-of-how-we-use-political-colors%2F&psig=AOvVaw1tL5UeACMye7NTm5hvZG-A&ust=1698159827386000&source=images&cd=vfe&opi=89978449&ved=0CBIQjhxqFwoTCKil57-4jIIDFQAAAAAdAAAAABAI)](../../assets/slides/imgs/1976_map.webp){#fig-1976-map}

@@

```{mermaid}
%%| label: fig-snap-judgment-model
%%| fig-cap: Overview of model

flowchart TD;
A[Detection of color] --> B[Activation of associated memories]
B --> C[Negative Valence]
B --> D[Positive Valence]
C -.-> E[Policy stance]
D -.-> F[Policy stance]
E -.-> G[Negative Valence]
E -.-> H[Positive Valence]
F -.-> I[Negative Valence]
F -.-> J[Positive Valence]
```

@@

# Define colors to detect
    #* White
        #** Not defined. Default for colorDetector()
    #* Red
republican_red = [232, 27, 35] # target color
red_lower = [93, 9, 12] # lower end of spectrum for red
red_higher = [255, 170, 170] # higher end of spectrum for red
